Verifying Demonstrations

### 2017-11-22 poster/contents-poster.tex
Removes files into separate directories

@@

    \begin{blackblock}{Technically, during protest}
      \begin{itemize}
        \item The organizer publishes the protest's manifesto.
        \item Each protester reads it, approves it, computes a protest (cause) 
          identifier (\(cid\)) to designate which protest they participate in.
        \item Each protester computes a personal identifier (\(pid\)), 
          unlinkable between protests,
        \item Each protester acts as witness (unlinkable between protesters) for 
          other protesters by creating participation-proof shares.
        \item Proof shares vouches for temporal and spatial eligibility.
        \item A threshold-based number of valid shares is a valid proof.
      \end{itemize}
    \end{blackblock}

    \begin{blackblock}{Technically, after the protest}
      \begin{itemize}
        \item Proof shares are committed to a blockchain as soon as possible.
        \item \Ac{NIZK} proofs of correctness of \(PRF\) computations and 
          validity of keys are submitted whenever convenient.
        \item Anyone can verify the proofs: eligibility, universal and 
          individual verifiability.
        \item Must be done for all shares and their \ac{NIZK} proofs.
        \item Count all \(pid\)s with valid proofs.
      \end{itemize}
    \end{blackblock}

>>>>

    \begin{blackblock}{Our scheme, during protest (\cref{ProofShare}, top of 
        \cref{Protocol})}
      \begin{itemize}
        \item The organizer publishes the protest's manifesto.
        \item Each protester reads it, approves it, computes a protest (cause) 
          identifier (\(cid\)) to designate which protest they participate in.
        \item Each protester computes a personal identifier (\(pid\)), 
          unlinkable between protests,
        \item Each protester acts as witness (\(wid\), unlinkable between 
          protesters, \(wsig\)) for other protesters by creating 
          participation-proof shares.
        \item Proof shares vouches for temporal and spatial eligibility.
        \item A threshold-based number of valid shares is a valid proof.
      \end{itemize}
    \end{blackblock}

    \begin{blackblock}{Our scheme, after the protest (bottom of 
        \cref{Protocol})}
      \begin{itemize}
        \item Proof shares are committed to a blockchain as soon as possible.
        \item \Ac{NIZK} proofs of correctness of \(PRF\) computations and 
          validity of keys are submitted whenever convenient.
        \item Anyone can verify the proofs: eligibility, universal and 
          individual verifiability.
        \item Must be done for all shares and their \ac{NIZK} proofs.
        \item Count all \(pid\)s with valid proofs.
      \end{itemize}
    \end{blackblock}

@@
